Introduction

This document presents univariate and bivariate tables   of environmental attitudes  among respondents of  Round 11 of the European Social Survey  (2023-24) 



```{r data}

rm(list=ls())

library(haven)
library(survey)
library(dplyr)
library(knitr)
library(gtsummary)
library(ggplot2)
library(weights)

source("syntax/functions.R")
source("syntax/labels_ess2_uk.R")

datadir<-"~/Data/ess/ESS11e04_1/"

ess.raw<-read_dta(paste0(datadir,"ESS11e04_1.dta")) 
ess<-droplevels(ess.raw |>
               select(all_of(c(ovars,exvars,auxvars,dvars,desvars))))

#######################################################################```
```



```{r recode}
source("syntax/recoding_ess2_uk.R")
``` 



## 1. Variables included 

|Name|Id|Variable label|Valid responses |
|----|--|---------------|----------------|
agegroup| - |`{r} attr(ess.raw$agegroup, "label")`|`{r} prettyNum(as.numeric(table(is.na(ess.raw$agegroup)))[1],big.mark = ",")`
ccnthum|C30|`{r} attr(ess.raw$ccnthum, "label")`|`{r} prettyNum(as.numeric(table(is.na(ess.raw$ccnthum)))[1],big.mark = ",")`
ccrdprs|C31|`{r} attr(ess.raw$ccrdprs, "label")`|`{r} prettyNum(as.numeric(table(is.na(ess.raw$ccrdprs)))[1],big.mark = ",")` 
cntry|-| `{r} attr(ess.raw$cntry, "label")` |`{r} prettyNum(as.numeric(table(is.na(ess.raw$cntry)))[1],big.mark = ",")` 
eisced|-| `{r} attr(ess.raw$eisced, "label")` |`{r} prettyNum(as.numeric(table(is.na(ess.raw$eisced)))[1],big.mark = ",")` 
gndr| - |`{r} attr(ess.raw$gndr, "label")`|`{r} prettyNum(as.numeric(table(is.na(ess.raw$gndr)))[1],big.mark = ",")`
hincfel|  -|`{r} attr(ess.raw$hincfel, "label")`|`{r} prettyNum(as.numeric(table(is.na(ess.raw$hincfel)))[1],big.mark = ",") `
lrscale|B26| `{r} attr(ess.raw$lrscale, "label")`|`{r} prettyNum(as.numeric(table(is.na(ess.raw$lrscale)))[1],big.mark = ",")`
wrclmch|C32| `{r} attr(ess.raw$wrclmch, "label")`|`{r} prettyNum(as.numeric(table(is.na(ess.raw$wrclmch)))[1],big.mark = ",")`

: **Table 1: Original and derived variables used in the analysis** {tbl-colwidths="[25,5,65,5]"}



  
## 2. Variables recoding and operationalisation notes

<!-- The original dataset includes `{r} prettyNum(nrow(ess.raw),big.mark = ",")` observations, of which `{r} prettyNum(nrow(ess),big.mark = ",")` respondents aged 50 and over. -->

<!-- 1. Integrated household composition variable  `hhdtypb`  was constructed using the household grid variables `rshipa*`, and household size information.  -->
<!-- 2. No information was available on the presence of grandchilddren -->
<!-- 3. There is no clear variable recording exclusively caring for dependents: it is either amalgamated with housework (`hwrk`) or with helping others more broadly: `hlpfmly`. -->
.<!-- 4. Whether respondents had internet connection was approximated using frequency of internet use. -->
<!-- 5. Marital status was constructed in order to include informal partnership/cohabitation. -->
<!-- 6. There are no variables measuring difficulties/limitations with daily life activities. A variable was constructed recording the number of health conditions instead.  -->




## 3. Univariates results

Results are presented as follows, under each tab below:
  
  1.  Unweighted frequencies and proportions of the original variables, unrecoded
  2.  Weighted frequencies and proportions of the recoded (ie missing/invalid values grouped together) variables


### 3.1 Univariates results overall


::: {.panel-tabset}


```{r univariates}
#| results: asis
#| echo: false


source("syntax/univariates_ess2.R")

```

### 3.2 Univariates results (by country)

:::: {.panel-tabset}


```{r univariates_c}
#| results: asis
#| echo: false


 source("syntax/univariates_country_ess2.R")

```


## 4. Outcome variables by sex, age, attitudes (overall)

This section contains for each variable used in the study, the following contingency tables:

  1. With voter turnout at the last national elections
  2. With sex
  3. With age, two and three categories

All contingency tables were computed with weighted data and include  $\chi^2$ test of independence.


### 4.1. Whether climate change is man-made 


::: {.panel-tabset}

```{r bivar1}
#| results: asis
#| echo: false

for (v in bivars19) {

cat(paste0("#### *Man made? by ",labs[[paste0(v,".f")]],"(",v, ")*"))
  
  
  tmp.t<-svytable(as.formula(paste0("~ccnthum.fr +", v,".fr")), ess.s)
  tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
  tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p,colSums(tmp.p))
  rownames(tmp.p)<-c("",rownames(tmp.t),"Total")
  names(tmp.p)<-c(rbind(colnames(tmp.t)," "))
  
  print(kable(tmp.p))
  cat('\n')
  
  
  # t<-svychisq(as.formula(paste0("~", v,".fr","+ ccnthum.fr")), ess.s)
  # print(t$method)
  # cat('\n')
  # 
  # print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))

  cat('\n')
  
  ################################################################################################
  
}

cat('\n:::')

```



### **4.2. Responsibility about climate change **




::: {.panel-tabset}

```{r bivar2}
#| results: asis
#| echo: false

for (v in bivars19) {
  
cat(paste0("#### *Responsibility by ",labs[[paste0(v,".f")]],"(",v, ")*"))

    
    tmp.t<-svytable(as.formula(paste0("~ccrdprs.fr + ", v,".fr")), ess.s)
    tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
    tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p,colSums(tmp.p))
  rownames(tmp.p)<-c("",rownames(tmp.t),"Total")
  names(tmp.p)<-c(rbind(colnames(tmp.t)," "))
    
    print(kable(tmp.p))
    cat('\n')
    
    # t<-svychisq(as.formula(paste0("~", v,".fr","+ ccrdprs.fr")), ess.s)
    # 
    # print(t$method)
    # cat('\n')
    # print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))
    
  cat('\n')
  
  ################################################################################################
  
}

cat('\n:::')

```

### **4.3. Worry about climate change  **

::: {.panel-tabset}

```{r bivar3}
#| results: asis
#| echo: false

for (v in bivars19) {

cat(paste0("#### *Worry by ",labs[[paste0(v,".f")]],"(",v, ")*"))
  
  
  tmp.t<-svytable(as.formula(paste0("~wrclmch.fr +", v,".fr")), ess.s)
  tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
  tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p,colSums(tmp.p))
  rownames(tmp.p)<-c("",rownames(tmp.t),"Total")
  names(tmp.p)<-c(rbind(colnames(tmp.t)," "))
  
  print(kable(tmp.p))
  cat('\n')
  
  
  # t<-svychisq(as.formula(paste0("~", v,".fr","+ wrclmch.fr")), ess.s)
  # print(t$method)
  # cat('\n')
  # 
  # print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))

  cat('\n')
  
  ################################################################################################
  
}

cat('\n:::')

```


## 5. Outcome variables by sex, age, attitudes (country level)


:::: {.panel-tabset}


```{r bicntry}
#| results: asis
#| echo: false

for (c in levels(as.factor(ess$cntry))) {

  
ess.s<-svydesign(~psu,weights=~anweight,strata=~stratum,data=ess|>filter(cntry==c),nest=T)
 
cat('### ', c, '\n')


cat('::: {.panel-tabset}')

cat('\n')
cat('\n')


for (v in ovars) {


#   cat('#### ', labs[[paste0(v,".f")]], '\n')

cat(paste0('#### ',labs[[paste0(v,".f")]],'\n'))

      cat('\n')

for (e in exvars) {
      cat('\n')

      cat('\n')

cat(paste0('**',labs[[paste0(e,".f")]],'**'))

      cat('\n')
      cat('\n')
  
  
    tmp.t<-svytable(as.formula(paste0("~droplevels(", v,".fr) + droplevels(", e,".fr)")), ess.s)
    tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
    tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p,colSums(tmp.p))
  rownames(tmp.p)<-c("",rownames(tmp.t),"Total")
  names(tmp.p)<-c(rbind(colnames(tmp.t)," "))

    print(kable(tmp.p))
    cat('\n')
    cat('\n')

}
    # t<-svychisq(as.formula(paste0("~", v,".fr","+ cntry.fr")), ess.s)
    #
    # print(t$method)
    # cat('\n')
    # print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))

  cat('\n')
    cat('\n')

  ################################################################################################


  }

cat('\n:::\n\n')


}

cat('\n::::')

```


## 6. Outcome variables (environmental attitudes)  by position on the left-right scale.


6.1 Overall

::: {.panel-tabset}


```{r leftright_overall}
#| results: asis
#| echo: false


  
ess.s<-svydesign(~psu,weights=~anweight,strata=~stratum,data=ess|>filter(cntry==c),nest=T)
 
#cat('### ', c, '\n')



cat('\n')
cat('\n')


for (v in ovars[-4]) {


#   cat('#### ', labs[[paste0(v,".f")]], '\n')

cat(paste0('### ',labs[[paste0(v,".f")]],'\n'))

      cat('\n')

#for (e in exvars) {
 #     cat('\n')

      cat('\n')

#cat(paste0('**',labs[[paste0(e,".f")]],'**'))

#      cat('\n')
#      cat('\n')
  
  
    tmp.t<-svytable(as.formula(paste0("~droplevels(", v,".fr) + droplevels(lrscale.fr)")), ess.s)
    tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
    tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p,colSums(tmp.p))
  rownames(tmp.p)<-c("",rownames(tmp.t),"Total")
  names(tmp.p)<-c(rbind(colnames(tmp.t)," "))

    print(kable(tmp.p))
    cat('\n')
    cat('\n')

#}
    # t<-svychisq(as.formula(paste0("~", v,".fr","+ cntry.fr")), ess.s)
    #
    # print(t$method)
    # cat('\n')
    # print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))

  cat('\n')
    cat('\n')

  ################################################################################################


  }


cat('\n:::\n\n')


```




6.2 By country

:::: {.panel-tabset}


```{r leftright_country}
#| results: asis
#| echo: false

for (c in levels(as.factor(ess$cntry))) {

  
ess.s<-svydesign(~psu,weights=~anweight,strata=~stratum,data=ess|>filter(cntry==c),nest=T)
 
cat('### ', c, '\n')


cat('::: {.panel-tabset}')

cat('\n')
cat('\n')


for (v in ovars[-4]) {


#   cat('#### ', labs[[paste0(v,".f")]], '\n')

cat(paste0('#### ',labs[[paste0(v,".f")]],'\n'))

      cat('\n')

#for (e in exvars) {
 #     cat('\n')

      cat('\n')

#cat(paste0('**',labs[[paste0(e,".f")]],'**'))

#      cat('\n')
#      cat('\n')
  
  
    tmp.t<-svytable(as.formula(paste0("~droplevels(", v,".fr) + droplevels(lrscale.fr)")), ess.s)
    tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
    tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p,colSums(tmp.p))
  rownames(tmp.p)<-c("",rownames(tmp.t),"Total")
  names(tmp.p)<-c(rbind(colnames(tmp.t)," "))

    print(kable(tmp.p))
    cat('\n')
    cat('\n')

#}
    # t<-svychisq(as.formula(paste0("~", v,".fr","+ cntry.fr")), ess.s)
    #
    # print(t$method)
    # cat('\n')
    # print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))

  cat('\n')
    cat('\n')

  ################################################################################################


  }

cat('\n:::\n\n')


}

cat('\n::::')

```



