## World Value Survey Wave 7

This page presents descriptive  tables  from the World Value Survey Wave 7, focusing on  left-right positionning and attitudes towards environmental breakdown.  
Below are  the list of variables used in the analysis, followed by uni- and bivariate tables, overall and by country.

```{r data}
rm(list=ls())

library(haven)
library(survey)
library(dplyr)
library(knitr)
library(gtsummary)
library(ggplot2)
library(weights)

datadir2<-"~/Data/wvs/"

source("syntax/functions.R")
source("syntax/labels_wvs.R")

wvs.raw<-read_dta(paste0(datadir2,"WVS_Cross-National_Wave_7_inverted_stata_v6_0.dta")) 
wvs<-droplevels(wvs.raw |>
               select(all_of(c(wovars7,wexvars7,wivars7,dvars7))))
```

## 1. Variables included in the analysis

|Name|Variable label|Valid responses |
|----|---------------|----------------|
C_COW_NUM| `{r} attr(wvs$C_COW_NUM, "label")` |`{r} prettyNum(as.numeric(table(is.na(wvs$C_COW_NUM>0)))[1],big.mark = ",")`
Q111|`{r} attr(wvs$Q111, "label")`|`{r} prettyNum(as.numeric(table((wvs$Q111>0)))[2],big.mark = ",")`
Q240|`{r} attr(wvs$Q240, "label")`|`{r} prettyNum(as.numeric(table((wvs$Q240>0)))[2],big.mark = ",")`
Q260|`{r} attr(wvs$Q260, "label")`|`{r} prettyNum(as.numeric(table((wvs$Q260>0)))[2],big.mark = ",")` 
Q275|`{r} attr(wvs$Q275, "label")` |`{r} prettyNum(as.numeric(table((wvs$Q275>0)))[2],big.mark = ",")` 
X003R|`{r} attr(wvs$X003R, "label")`|`{r} prettyNum(as.numeric(table((wvs$X003R>0)))[2],big.mark = ",")`


: **Table 1: Original and derived variables used in the analysis** {tbl-colwidths="[25,70,5]"}


```{r recode}
source("syntax/recoding_wvs7.R")
```


## 2. Univariates results

### 2.1 Overall


::: {.panel-tabset}



```{r univ}
#| output: asis
  
source("syntax/univariates_wvs7.R")

```


### 2.2 By country

:::: {.panel-tabset}


```{r univariates_c}
#| results: asis


source("syntax/univariates_country_wvs7.R")

```


## 3. Outcome variables by sex, age, education - overall (weighted)

### 3.1 Overall


::: {.panel-tabset}

```{r bivar1}
#| results: asis
#| echo: false

for (v in wexvars7) {

cat(paste0("#### Crosstab by",labs7[[paste0(v,".f")]],"(",v, ")"))
  
cat('\n')  
cat("**Left-right political scale**")
cat('\n')

  tmp.t<-svytable(as.formula(paste0("~Q240.fr +", v,".fr")), wvs.s)
  tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
  tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p,colSums(tmp.p))
  rownames(tmp.p)<-c("",rownames(tmp.t),"Total")
  names(tmp.p)<-c(rbind(colnames(tmp.t)," "))
  
  print(kable(tmp.p))
  cat('\n')
  
  
  # t<-svychisq(as.formula(paste0("~", v,".fr","+ ccnthum.fr")), ess.s)
  # print(t$method)
  # cat('\n')
  # 
  # print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))

  cat('\n')
  cat('\n')
  cat('\n')
  
  ################################################################################################

#cat(paste0("#### *Protecting environment vs. Economic growth by ",labs7[[paste0(v,".f")]],"(",v, ")*"))
cat("**Protecting environment vs. Economic growth**")
  
cat('\n')
  
  tmp.t<-svytable(as.formula(paste0("~Q111.fr +", v,".fr")), wvs.s)
  tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
  tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p,colSums(tmp.p))
  rownames(tmp.p)<-c("",rownames(tmp.t),"Total")
  names(tmp.p)<-c(rbind(colnames(tmp.t)," "))
  
  print(kable(tmp.p))
  cat('\n')
  
  
  # t<-svychisq(as.formula(paste0("~", v,".fr","+ ccnthum.fr")), ess.s)
  # print(t$method)
  # cat('\n')
  # 
  # print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))


  
  
  # t<-svychisq(as.formula(paste0("~", v,".fr","+ ccnthum.fr")), ess.s)
  # print(t$method)
  # cat('\n')
  # 
  # print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))

  cat('\n')
    

}

cat('\n:::')

```


### 3.2 Overall  Outcome variables by sex, age, education (weighted) - country level


:::: {.panel-tabset}


```{r bicntry}
#| results: asis
#| echo: false

for (c in levels(wvs$C_COW_NUM.f)) {

wvs.s<-svydesign(~1,weights=~W_WEIGHT,data=wvs |> filter(C_COW_NUM.f==c)|> droplevels(),nest=T)
 
cat('### ', c, '\n')


cat('::: {.panel-tabset}')

cat('\n')


for (v in wovars7) {


#   cat('#### ', labs7[[paste0(v,".f")]], '\n')

cat(paste0('#### ',labs7[[paste0(v,".fr")]],'\n'))

cat('\n')

for (e in bivars7) {

cat('\n')

cat(paste0('**',labs7[[paste0(e,".fr")]],'** \n'))


  
tmp.t<-svytable(as.formula(paste0("~", v,".fr + ", e,".fr")), wvs.s)
tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p,colSums(tmp.p))
rownames(tmp.p)<-c("",rownames(tmp.t),"Total")
names(tmp.p)<-c(rbind(colnames(tmp.t)," "))

print(kable(tmp.p))
cat('\n')

}
    # t<-svychisq(as.formula(paste0("~", v,".fr","+ cntry.fr")), ess.s)
    #
    # print(t$method)
    # cat('\n')
    # print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))

  cat('\n')


  ################################################################################################


  }

cat('\n:::\n\n')


}

cat('\n::::')
    cat('\n')
```


## 4. Environmental views by left-right position (weighted)


### 4.1 Overall
```{r lr}
#| results: asis
#| echo: false

wvs.s<-svydesign(~C_COW_NUM,weights=~W_WEIGHT,data=wvs,nest=T)
tmp.t<-svytable(~Q111.fr + Q240.fr, wvs.s)
tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p,colSums(tmp.p))
rownames(tmp.p)<-c("",rownames(tmp.t),"Total")
names(tmp.p)<-c(rbind(colnames(tmp.t)," "))

print(kable(tmp.p))
cat('\n')
```
### 4.2 Country-level

::: {.panel-tabset}

```{r lrcountry}
#| results: asis
#| echo: false

for (c in levels(wvs$C_COW_NUM.f)) {

  wvs.s<-svydesign(~1,weights=~W_WEIGHT,data=wvs |> filter(C_COW_NUM.f==c)|> droplevels(),nest=T)
  

    
cat('#### ', c, '\n')
  
  

tmp.t<-svytable(~Q111.fr + Q240.fr, wvs.s)
tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p,colSums(tmp.p))
rownames(tmp.p)<-c("",rownames(tmp.t),"Total")
names(tmp.p)<-c(rbind(colnames(tmp.t)," "))

print(kable(tmp.p))
cat('\n')



cat('\n')
  
  
  
}

cat('\n:::')

cat('\n')
```
